resistanceModelNotesAndy

### 2016-02-09 resistanceModelNotesAndy.Rmd
notes

@@

~ rerun the trees for Ian

~ set 10000 runs going before yoga, but whether extended or normal curtis ?

~ I might be able to do a PRCC of whether mixtures better than sequential (but actually thats what the trees do)

>>>>

Instead I saved the original random value of exposure and used that in PRCC.

I think what was happening was that correctDeployProp influenced the AB exposure value for mixtures and that was the predictor I took for exposure. Instead I want the intended exposure value.

I still don't quite understand how this effects the results in the single insecticide runs.

but with my 100 test runs what I'm seeing in the PRCC is no effect of anything for insect1 & 2. and a similar pattern as before for mixture1.

This may point me towards another problem that is causing this.
I may need to exclude corectDeploy as a predictor from those runs in which it wasn't used ??

** 2/2/16 **

~ ran 10000 runs over night
~ run effectOfIndividualInputs
~ now it's fine !!! PRCC looking good.

New trees from 10,000 : 
Predictors :
effectiveness_insecticide1 :9
effectiveness_insecticide2 :9
exposure :                  7

dominance_allele2 :         3
dominance_allele1 :         4
resist_start_1_div_2 :      1
start_freq_allele2 :        1
start_freq_allele1 :        2

Best tree to show (if indeed trees are the best) : 
Can't find a best one ! I don't like these trees !!
Try to find a better method for Ian. Could it be PRCC.

Violin plots. look good. They are very similar for time to resistance 0.1, 0.25 or 0.5. 
~ need a plot of proportion of runs in which mixture or sequential better. Maybe I could do a violin plot of the time to threshold, with diff strategies on x axis.

~ faceting them by exposure is cool
~ faceting by effectivity shows very little

** 5/2/16 **

trying to get plots working

## GOOD RESULTS ! :

###1 effectiveness < 0.6 sequential best. > 0.6 mix best. 
Plot of time_to_resistance against effectiveness  with 4 strategies on the same plot is key.

It shows the line for mix2 crossing that of sequential. Effectiveness 0.4-0.6 resistance arises faster for mix2. > 0.6 resistance arises faster for sequential.

I should adapt this plot perhaps just to show mix2 and sequential.

###2 selection coeff < 0.2 sequential best. > 0.2 mix best.
selection coefficient curves also cross for mix2 and sequential. < ~0.2 sequential is better. > 0.2 mixture is better. 
But check that this is multiplied as shown below. So beware could this be caused by the effectiveness result ?
    ##effectiveness
    phi.SS1_A0 <- runif(1, min=0.4, max=1)
    phi.SS2_0B <- runif(1, min=0.4, max=1)

    # Ian suggested this should be dependent on effectiveness to ensure fitness of RR stays below 1 
    s.RR1_A0 <- runif(1, min=0.2, max=1) * phi.SS1_A0
    s.RR2_0B <- runif(1, min=0.2, max=1) * phi.SS2_0B

I think perhaps I should remove multiplication of selection coefficient by effectiveness ?

###3
Effect of exposure is greater overall on times to resistance, but it has a more similar effect on mixtures & sequential thus it is of less importance when considering the differences between the two strategies.

In majority of cases the point where resistance to just one of the insecticides in a mixture is reached comes before that for both insecticides in sequential use. [this seems obvious]
Also it always takes longer to reach resistance for both insecticides when starting with both in a mixture. Is this obvious, or a meaningfull result or an error in our methodology ?

I think for the paper we should focus on mix2 versus sequential. We could have that as what we call mixture, and then refer in smallere analyses to the other mix scenarios.
Maybe I should have a quick look at curtis paper to remind myself ?

Tried removing multiplication of selection coefficient by effectiveness.
But got warnings about fitnesses > 1.

6/2/16

problem is with locus fitness values going over 1

This is the problem that causes it :

Wloci[ paste0('RR',locusNum), exposure] <- (1 - phi[locusNum, exposure]) + 
                                                   (s[locusNum, exposure])

so it just occurs when s > phi, selection coeff > effectiveness

current range :
effectiveness : 0.4 - 1
selection coeff : 0.2 - 0.5

Options : 
1) discard sims in which selection > effectiveness
2) set selection range to 0.1-0.45 and effectiveness from 0.45-1

Doing 2) might be good to check whether the line crossing still goes on ...

Yes saving 2) as listOutMix_ex2_1000.rda etc.

 Done in effectOfIndividualInputs

** 7/2/16 **
with new runs

Selection coefficient curves for mix2 & sequential no longer cross. Seems likely that this previous pattern was generated by correlation with effectiveness.

@@

~ run PRCC for difference between mix2 & sequential
~ might need to structure data differently

Tighten up the story before sending to Ian, I'm getting there. Maybe put into a summary Rmd pdf.

## IDEA
# rather than trees of e.g. mix1 better than sequence I could show time-to-resistance mix1-sequence.

OR I could even put time_to_resistance on the same plot for each stratgey (maybe with exposure on the x-axis)
This is very similar to some plots I have already, I just need to remove the facetting by strategy and remove individual strategies.

## BEWARE what am I doing with putting mixture better than seq on each repeated input ....  
## e.g. it doesn't seem to quite make sense that I have mixture or sequence better for insecticide1
## but maybe it is because all the inpiuts are repeated

## might be good to facet by mixture sequence better and just have points of x=exposure, y=effectiveness_insecticide1

~ do PRCCs on whether mixture or sequential better

~ tomorrow when on good form in morning work out how best to summarise for Ian

~ add other resist thresholds into PRCC.

~ can I get plots to show just a subset of points ?

~ produce a graphich of the 3 diff mixture scenarios & sequential
~~ may be able to use the seriousGame plot method
~~ I could even show resistance curves next to it ?

### My summary of results & thoughts

Resistance to two insecticides arises more slowly if they are used in combination rather than sequentially. See violin plots.
